Balsa: A Compact Line Notation Based on SMILES

### 2023-01-04 manuscript.tex
Excludes trailing branches. Closes #57

An alternative to \ttt{union} within a sequence is the \ttt{branch} non-terminal (\enquote{branch}). Like union, branch joins a parent and child node. Wrapped by opening and closing parenthesis terminals (\enquote{(} and \enquote{)} respectively), branch encodes a sequence that may or may not be bonded to its parent. Bonding occurs if the \ttt{bond} non-terminal is included. Alternatively, the sequence will not be bonded if the \ttt{dot} non-terminal (\enquote{.}) appears. If neither \ttt{bond} nor \ttt{gap} are present, parent and child are connected through an elided bond.

\begin{lstlisting}
branch ::= "(" ( dot | bond )? sequence ")"
\end{lstlisting}

>>>>

An alternative to \ttt{union} within a sequence is the \ttt{branch} non-terminal (\enquote{branch}). Like union, branch joins a parent and child node. Wrapped by opening and closing parenthesis terminals (\enquote{(} and \enquote{)} respectively), the first part of \ttt{branch} expects a sequence that may or may not be bonded to its parent. Bonding occurs if the \ttt{bond} non-terminal is included. Alternatively, the sequence will not be bonded if the \ttt{dot} non-terminal (\enquote{.}) appears. If neither \ttt{bond} nor \ttt{gap} are present, parent and child are connected through an elided bond. The second part of \ttt{branch} expects one of either a union or branch. This ensures that strings terminated with a branch, or containing a gap after a branch will be rejected.

\begin{lstlisting}
branch ::= "(" ( dot | bond )? sequence ")"
           ( union | branch)+
\end{lstlisting}
